### 2018-10-08 tex/evaluation.tex
update
version 0.1

\begin{figure*}
	\includegraphics[width=0.85\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}
\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{fig/sampling}
	\caption{Sampling Overhead}
	\label{fig:sampling}
	\vspace{-1em}
\end{figure}

@@

We also implemented Scache on Hadoop MapReduce to verify the universality of SCache. We use Terasort to evaluate the performance of scache on Hadoop MapReduce. Terasort's implementation of Hadoop Mapreduce only includes one Shuffle process from the Map phase to the Reduce phase. Terasort is a task that requires a lot of data shuffle. All input data for the Job will be shuffled.

Figure \ref{fig:hadoop_terasort_origin} shows the hardware resource utilization of the original Hadoop Mapreduce running Terasort. Figure \ref{fig:hadoop_terasort_scache} shows the hardware resource utilization with SCache. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 25\% of total time optimization with input data size 256GB. Without SCache, Hadoop writes intermediate data locally in the Map phase. Hadoop began to shuffle in the reduce stage. Because the large amount of shuffle data reaches the network bottleneck, Hadoop needs to wait for network transfer in the front of reduce stage. This causes the CPU resources to be idle. As shown in the Figure \ref{fig:hadoop_terasort_scache}, the job with SCache pre-fetch shuffle data in the Map phase. This avoids the job waiting for the shuffle transmission in the Reduce phase. Furthermore, prefetching shuffle data utilize the idle IO throughput in the Map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize job completion time by up to 25\% and an average of 15\% with input data sizes from 128GB to 512GB.
}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.85\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}
\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{fig/sampling}
	\caption{Sampling Overhead}
	\label{fig:sampling}
	\vspace{-1em}
\end{figure}

@@

To prove SCache compatibility as a plug-in, we also implemented Scache on Hadoop MapReduce as the external shuffle service and co-scheduler. Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing such as Hadoop MapReduce, some shuffle-heavy job on Hadoop can still be optimized.

Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop Mapreduce running Terasort. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 15\% of total time optimization with input data size 384GB. Without SCache, Hadoop writes intermediate data locally in the Map phase. Hadoop began to shuffle in the reduce stage. Because the large amount of shuffle data reaches the network bottleneck, Hadoop needs to wait for network transfer in the front of reduce stage. This causes the CPU resources to be idle. As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching and pre-scheduling in the Map phase. This avoids the Reduce phase waiting for the shuffle data. Furthermore, pre-fetching  utilize the idle IO throughput in the Map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize Terasort completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
}

### 2018-10-08 tex/intro.tex
version 0.1

@@

We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.

>>>>

{\color{blue}
In order to visually describe above-mentioned resources scheduling and analyze deficiencies, we propose \textit{Framework Resources Quantification}(FRQ) model. FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension. We use FRQ model to help us analyze the deficiencies of resources scheduling and optimize it.
}

@@

{\color{red}
We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
}

{\color{blue}
We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop. We have also designed a mathematic model called \textit{Framework Resources Quantification}(FRQ) model. We use FRQ model to analyze the principle of SCache and calculate the time of each phase of computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
